\textit{Introduction}

Here's the introduction

\subsection{What this work is not}

\subsection{A Use Case}

\subsection{The Bare Bones}
Data Infrastructure Needs for the Materials Genome Initiative:
\begin{enumerate}
\item Some sort of interface/api that the user interacts with to deposit their information such that (2) is enabled.  This entails
\begin{enumerate}
\item The establishment of repositories to store the data
\item The reposed data should then be marked up with sufficient metadata to inform someone else how the data was created, including attribution or provenance information relevant to citation 
(There is a likely role for standard metadata schemes for certain types of data in this requirement)
\item	Assignment of a persistent digital identifier (like the DOI for journals) so the data can be cited and discovered by others
\item Assignment of terms of use for the data (licenses), for both the creator of the data and the repository
\end{enumerate}
\item 
\end{enumerate}

e.	Tools must be developed to
i.	enable the ingest of data from computation or experiment for deposition in a repository
ii.	simplify metadata collection, e.g. by
1.	Automatically assigning some basic metadata
2.	Implementing automatic extraction of metadata to the extent possible 
iii.	Assign persistent digital identifiers
2.	Some sort of interface/api that the user interacts with to find needed information.  This requires (at least)
a.	the registration of the availability of the data into some sort of “registry” to enable discovery without prior knowledge of the existence of the repository/specific data features.
b.	Various types of policy enforcement  
c.	Terminologies and ontologies to enhance search 
d.	Tools to enable assessments of the relevance of the data to the question at hand, such as quick-look plotting or imaging capabilities



The technologies to do items 1+2 are not well developed in materials science.  That is, if you were to do a Google search for X-ray data for a particular crystal, the results would be highly uneven at best, and largely worthless some of the time.  Let’s start by addressing (2).  We assume a researcher is developing a new material, and in order to do that, he needs a baseline of the existing materials data and models that will enable this design.  

